A numerical study of variational data assimilation for the wave equation in heterogeneous media

### 2024-12-07 tex/main.tex
minors

\begin{proof}
    Due to the assumption that $c_i \in C^\infty(\Omega_i)$, $i = 1,2$, there exists $C > 0$ s.t.  
    \begin{equation*}
        \tnorm{(\Uh - \Vh, 0)}_{\wop} \le C \tnorm{(\Uh - \Vh, 0)}_{\square_1},
    \end{equation*}
    where $\tnorm{(\cdot, \cdot)}_{\square_1}$ is defined by \eqref{eq:tnormwop} with $c_i = 1$, $i = 1,2$. Thus, we can apply the interpolation results derived in \cite[Lem. 2.4]{BP24} to obtain the claim. 
\end{proof}

@@

\begin{proof}
    The proof follows from the same argumentation as the proof of \cite[Thm. 4.4]{BP24}.
\end{proof}

@@

\begin{rmk}
    Suppose that Assumption \ref{assum:LipschitzStability} is not satisfied, e.g. if the GCC is not fulfilled. If $T$ is large enough such that \eqref{eq:Tcondition} holds, we can still apply the results from Thm. \ref{thm:filippas}. To utilize this result similarly to Assumption \ref{assum:LipschitzStability}, we would have to deal with the following technicalities:  
    \begin{enumerate}
        \item The results from Thm. \ref{thm:filippas} are formulated in terms of $\Vert \wop u \Vert_{L^2(Q)}$. However, we can only control $\Vert \wop \tilde{e}_h \Vert_{H^{-1}(Q)}$ for the residual $\tilde{e}_h = u - L_{\Delta t} \ul_1$. Thus, we would have to rewrite the estimates from Thm. \ref{thm:filippas} with $\Vert \wop u \Vert_{H^{-1}(Q)}$ instead of $\Vert \wop u \Vert_{L^2(Q)}$. To this end, one might be able to shift the regularity suitably, cf. \cite[Sec. 2.6]{StolkPhD}, or use similar arguments as in \cite[Thm. A.1]{BFMO21}.
        \item We have to ensure that the constants in the estimates from Thm. \ref{thm:filippas} remain bounded when we consider the residual $\tilde{e}_h$. In particular, we have to control $C_{0,1} := \Vert (\tilde{e}_h \vert_{t = 0}, \dt \tilde{e}_h \vert_{t = 0}) \Vert_{H^1 \times L^2}$. We note that we can always ensure that $C_{0,1}$ is bounded by adding a suitable Tikhonov regularization term to \eqref{eq:primalStab}. 
    \end{enumerate}
    Then, we can use the arguments of \cite[Thm. 4.4]{BP24} to show that 
    \begin{equation}
        \Vert (u - \ul_1) \vert_{t = 0} \Vert_{L^2(\Omega)}  + \Vert \dt (u - \ul_1) \vert_{t = 0} \Vert_{H^{-1}(\Omega)} \le C C_{0,1} \log(1 + C_{0,1} h^{-s} \Vert u \Vert_{H^m(Q)}^{-1})^{-1}. 
    \end{equation}
\end{rmk}

\section{Numerical experiments}
\noindent In this section, we present numerical experiments carried out with the proposed method. The examples are implemented using the \texttt{FEniCSx} library \cite{BarattaEtal2023,BasixJoss,ScroggsEtal2022,AlnaesEtal2014}. 
~\jp{We need to setup some reproduction material.}

\subsection{Examples in one space dimension}
\noindent We consider the unit interval $\Omega \coloneqq [0,1] \subset \mathbb{R}$. For a refinement level $L \in \mathbb{N}$, we partition the domain into $2^{L+1}$ uniform elements such that $h = 1/2^{L+1}$. The time step is chosen as $\Delta t = h$.

@@

>>>>

\begin{proof}
    Due to the assumption that $c_i \in C^\infty(\Omega_i)$, $i = 1,2$, there exists $C > 0$ s.t.  
    \begin{equation*}
        \tnorm{(\Uh - \Vh, 0)}_{\wop} \le C \tnorm{(\Uh - \Vh, 0)}_{\square_1},
    \end{equation*}
    where $\tnorm{(\cdot, \cdot)}_{\square_1}$ is defined by \eqref{eq:tnormwop} with $c_i = 1$, $i = 1,2$. Thus, we can apply the interpolation results derived in \cite[Lemma 5]{BP24} to obtain the claim. 
\end{proof}

@@

\begin{proof}
    The proof follows from the same argumentation as the proof of \cite[Theorem 10]{BP24}.
\end{proof}

@@

\begin{rmk}
    Suppose that Assumption \ref{assum:LipschitzStability} is not satisfied, e.g. if the GCC is not fulfilled. If $T$ is large enough such that \eqref{eq:Tcondition} holds, we can still apply the results from Thm. \ref{thm:filippas}. To utilize this result similarly to Assumption \ref{assum:LipschitzStability}, we would have to deal with the following technicalities:  
    \begin{enumerate}
        \item The results from Thm. \ref{thm:filippas} are formulated in terms of $\Vert \wop u \Vert_{L^2(Q)}$. However, we can only control $\Vert \wop \tilde{e}_h \Vert_{H^{-1}(Q)}$ for the residual $\tilde{e}_h = u - L_{\Delta t} \ul_1$. Thus, we would have to rewrite the estimates from Thm. \ref{thm:filippas} with $\Vert \wop u \Vert_{H^{-1}(Q)}$ instead of $\Vert \wop u \Vert_{L^2(Q)}$. To this end, one might be able to shift the regularity suitably, cf. \cite[Sec. 2.6]{StolkPhD}, or use similar arguments as in \cite[Thm. A.1]{BFMO21}.
        \item We have to ensure that the constants in the estimates from Thm. \ref{thm:filippas} remain bounded when we consider the residual $\tilde{e}_h$. In particular, we have to control $C_{0,1} := \Vert (\tilde{e}_h \vert_{t = 0}, \dt \tilde{e}_h \vert_{t = 0}) \Vert_{H^1 \times L^2}$. We note that we can always ensure that $C_{0,1}$ is bounded by adding a suitable Tikhonov regularization term to \eqref{eq:primalStab}. 
    \end{enumerate}
    Then, we can use the arguments of \cite[Theorem 10]{BP24} to show that 
    \begin{equation}
        \Vert (u - \ul_1) \vert_{t = 0} \Vert_{L^2(\Omega)}  + \Vert \dt (u - \ul_1) \vert_{t = 0} \Vert_{H^{-1}(\Omega)} \le C C_{0,1} \log(1 + C_{0,1} h^{-s} \Vert u \Vert_{H^m(Q)}^{-1})^{-1}. 
    \end{equation}
\end{rmk}

\section{Numerical experiments}
\noindent In this section, we present numerical experiments carried out with the proposed method. The examples are implemented using the \texttt{FEniCSx} library \cite{BarattaEtal2023,BasixJoss,ScroggsEtal2022,AlnaesEtal2014}. 
~\jp{We need to prepare some reproduction material.}
\subsection{Examples in one space dimension}
\noindent We consider the unit interval $\Omega \coloneqq [0,1] \subset \mathbb{R}$. For a refinement level $L \in \mathbb{N}$, we partition the domain into $2^{L+1}$ uniform elements such that $h = 1/2^{L+1}$. The time step is chosen as $\Delta t = h$.

@@

\section{More material}
